---
title: "BRT Analysis"
author: "Anna Talucci"
date: "September 2, 2019"
output: html_document
---

# Overview

## Notes

9-2-2019 Run wi sampling from updated gee code that should match the 5-15-2019 version.

Final Models
Full Model
Simple Model


--Beetle vs. Fuels

Boosted Regression Trees in R 
Note: this is a cut-down version of a tutorial prepared by Jane Elith and John Leathwick
Adapted by Chris Dunn for fire risk assessment
Adapted by Garrett Meigs for analysis of fire refugia
Complementary to Krawchuk et al. 2016 Ecosphere scripts



# Clear workspace

```{r}
rm(list=ls()) 
```


## Set libraries
```{r include=FALSE}

library(devtools)
library(gbm)
library(foreign)
library(dismo)
library(dplyr)
library(splines)
library(ggplot2)
```

##Install additional BRT functions 
These are provided in a file such as ?brt.functions.R? and can be loaded into R using the source command, e.g.:
```{r}
source("../function/brt.functions.R")
```

# Import data
```{r}
model.data = read.csv("../data/GRTS_Samples/2019-09-02_AllSamples.csv", header=TRUE, sep = ",", strip.white = TRUE)
```

# Check dimensions, column names and order for later operations, and summary statistics
```{r}
head(model.data)
```

```{r}
summary(model.data$nbrprefire)
```
```{r}
summary(model.data$ndmiprefire)
```
```{r}
summary(model.data$ndviprefire)
```

```{r}
summary(model.data$ndmibeetle)
```
```{r}
summary(model.data$ndmimeanbeetle)
```

```{r}
summary(model.data$ndvibeetle)
```



```{r}
dim(model.data)
```
```{r}
hist(model.data$fwi)
```


## Subset by FWI
presence/absence (1/0) of high burn severity 
```{r}
model.data$fwi_lohi = ifelse(model.data$fwi <= 29, 1, 2)
model.data$reclass_rdnbr_mt = ifelse(model.data$rdnbr < 316, 0, 1)
model.data$reclass_rdnbr_fs = ifelse(model.data$rdnbr < 600, 0, 1)
 
```
2 is anything greater then 29 and 1 is anything less than or equal to 29
```{r}
head(model.data)
```

```{r}
dim(model.data)
```

```{r}
model.data.lo = subset(model.data, fwi_lohi == "1")
```

```{r}
dim(model.data.lo)
```
```{r}
model.data.lo %>%
  count(reclass_rdnbr_fs) %>%
  group_by(reclass_rdnbr_fs) 
```

```{r}
model.data.hi = subset(model.data, fwi_lohi == "2")
```

```{r}
dim(model.data.hi)
```

```{r}
model.data.hi %>%
  count(reclass_rdnbr_fs) %>%
  group_by(reclass_rdnbr_fs) 
```


```{r}
head(model.data)
```

```{r}
names(model.data)
```


# MODEL F1 & F2


## Model F1: Split FWI - FWI HI 
Run the BRT model
with explanatory variables: 
*  dndmi (15)
*  elevation(17)
*  fwi (18)
*  ndviprefire (21)
*  rdnbr_class(26)
*  reclass_rdnbr_mt (34)
*  reclass_rdnbr_fs (35)

```{r}
set.seed(15) # Set random seed
brt.modelF1 <- gbm.step(data=model.data.hi,
    gbm.x = c(15,17,18,21), ## 11 variables
    gbm.y = 35,
    family = "bernoulli",
    tree.complexity = 5,
    learning.rate = 0.001,
    bag.fraction = 0.5)
```

### Get info in model output
```{r}
summary(brt.modelF1,
        cBars=length(brt.modelF1$var.names),
        n.trees=brt.modelF1$n.trees,
        plotit=TRUE,
        order=TRUE,
        method=relative.influence,
        normalize=FALSE)
```

### Save model output as external object for mapping later or posterity

```{r}
save(brt.modelF1, file = "../output/finalmodels_mt/BRTF1_model_data_output.rda")
```

```{r eval=FALSE, include=FALSE}
load(file = "../output/finalmodels/BRTF1_model_data_output.rda")
```

### Relative influence of predictors as part of summary gbm - for model assessment
```{r}
relative.influence(brt.modelF1, scale=TRUE, sort=TRUE)
```

Notes: permutation.test.gbm(brt.model, n.trees=brt.model$n.trees); This method randomly permutes each predictor variable at a time and computes the associated reduction in predictive performance, similar to random forests. gbm.loss(y,f,w,offset,dist,baseline, group, max.rank)

### Plotting (Anna Added)
```{r}
gbm.plot(brt.modelF1, smooth=TRUE, write.title = FALSE)
dev.print(pdf, "../figs/finalmodels_mt/2019-09-02_BRT_modelF1_plots.pdf")
dev.off()
```
```{r}
gbm.plot.fits(brt.modelF1)
dev.print(pdf, "../figs/finalmodels_mt/2019-09-02_BRT_modelF1_fits_plots.pdf")
dev.off()
```

```{r}
find.int = gbm.interactions(brt.modelF1)
find.int$rank.list
find.int$interactions
```

## Calculate output stats 
- Sandra Haire calculations and file export below from Krawchuk et al. (2016) Ecosphere
Note that these calculatins are not the same as the default outputs from the BRT code.
```{r}
tot.n=nrow(model.data.hi)
y.perc=round(nrow(model.data.hi[model.data.hi$yvar==1,])/tot.n,2)
vnames=row.names(brt.modelF1$contributions)
rel.inf=round(brt.modelF1$contributions[,2],2) # variable num, from df and %contrib for each
perc.dev.expl=round(1-(brt.modelF1$self.statistics$mean.resid/brt.modelF1$self.statistics$mean.null),2)
roc.mean=round(mean(brt.modelF1$cv.roc.matrix),2)
cv.dev.mean=round(brt.modelF1$cv.statistics$deviance.mean,2)
cv.cor.mean=round(brt.modelF1$cv.statistics$correlation.mean,2)
cv.discrim.mean=round(brt.modelF1$cv.statistics$discrimination.mean,2)
```

```{r}
BRT.modelF1.sum=data.frame(tot.n, y.perc, brt.modelF1$n.trees, perc.dev.expl, roc.mean, cv.dev.mean, cv.cor.mean, cv.discrim.mean)
write.csv(BRT.modelF1.sum, '../output/finalmodels_mt/2019-09-02_BRT_modelF1_sum.csv', row.names = F)
BRT.modelF1.relinf=data.frame(rel.inf, vnames)
write.csv(BRT.modelF1.relinf, '../output/finalmodels_mt/2019-09-02_BRT_modelF1_relinf.csv', row.names = F)
```

```{r}
BRT.modelF1.sum
```

```{r}
BRT.modelF1.relinf
```

## Model F2: Split FWI - FWI Lo 
Run the BRT model with explanatory variables: dndmi (15), elevation(17), fwi (18), ndviprefire (21), rdnbr_class(26), reclass_rdnbr_mt (34), reclass_rdnbr_fs (35)

```{r}
set.seed(15) # Set random seed
brt.modelF2 <- gbm.step(data=model.data.lo,
    gbm.x = c(15,17,18,21), 
    gbm.y = 35,
    family = "bernoulli",
    tree.complexity = 5,
    learning.rate = 0.001,
    bag.fraction = 0.5)
```

### Get info in model output
```{r}
summary(brt.modelF2,
        cBars=length(brt.modelF2$var.names),
        n.trees=brt.modelF2$n.trees,
        plotit=TRUE,
        order=TRUE,
        method=relative.influence,
        normalize=FALSE)
```

### Save model output as external object for mapping later or posterity

```{r}
save(brt.modelF2, file = "../output/finalmodels_mt/BRTF2_model_data_output.rda")
```

```{r eval=FALSE, include=FALSE}
load(file = "../output/finalmodels_mt/BRTF2_model_data_output.rda")
```

### Relative influence of predictors as part of summary gbm - for model assessment
```{r}
relative.influence(brt.modelF2, scale=TRUE, sort=TRUE)
```

Notes: permutation.test.gbm(brt.model, n.trees=brt.model$n.trees); This method randomly permutes each predictor variable at a time and computes the associated reduction in predictive performance, similar to random forests. gbm.loss(y,f,w,offset,dist,baseline, group, max.rank)

### Plotting (Anna Added)
```{r}
gbm.plot(brt.modelF2, smooth=TRUE, write.title = FALSE)
dev.print(pdf, "../figs/finalmodels_mt/2019-09-02_BRT_modelF2_plots.pdf")
dev.off()
```
```{r}
gbm.plot.fits(brt.modelF2)
dev.print(pdf, "../figs/finalmodels_mt/2019-09-02_BRT_modelF2_fits_plots.pdf")
dev.off()
```

```{r}
find.int = gbm.interactions(brt.modelF2)
find.int$rank.list
find.int$interactions
```

## Calculate output stats 
- Sandra Haire calculations and file export below from Krawchuk et al. (2016) Ecosphere
Note that these calculatins are not the same as the default outputs from the BRT code.
```{r}
tot.n=nrow(model.data.lo)
y.perc=round(nrow(model.data.lo[model.data.lo$yvar==1,])/tot.n,2)
vnames=row.names(brt.modelF2$contributions)
rel.inf=round(brt.modelF2$contributions[,2],2) # variable num, from df and %contrib for each
perc.dev.expl=round(1-(brt.modelF2$self.statistics$mean.resid/brt.modelF2$self.statistics$mean.null),2)
roc.mean=round(mean(brt.modelF2$cv.roc.matrix),2)
cv.dev.mean=round(brt.modelF2$cv.statistics$deviance.mean,2)
cv.cor.mean=round(brt.modelF2$cv.statistics$correlation.mean,2)
cv.discrim.mean=round(brt.modelF2$cv.statistics$discrimination.mean,2)
```

```{r}
BRT.modelF2.sum=data.frame(tot.n, y.perc, brt.modelF2$n.trees, perc.dev.expl, roc.mean, cv.dev.mean, cv.cor.mean, cv.discrim.mean)
write.csv(BRT.modelF2.sum, '../output/finalmodels_mt/2019-09-02_BRT_modelF2_sum.csv', row.names = F)
BRT.modelF2.relinf=data.frame(rel.inf, vnames)
write.csv(BRT.modelF2.relinf, '../output/finalmodels_mt/2019-09-02_BRT_modelF2_relinf.csv', row.names = F)
```

```{r}
BRT.modelF2.sum
```

```{r}
BRT.modelF2.relinf
```

# MODEL F3 & F4: Remove outbreak severity variable.


## Model F3: Split FWI - FWI HI 
Run the BRT model
with explanatory variables: dndmi (15), elevation(17), fwi (18), ndviprefire (21), rdnbr_class(26), reclass_rdnbr_mt (34), reclass_rdnbr_fs (35)

```{r}
set.seed(15) # Set random seed
brt.modelF3 <- gbm.step(data=model.data.hi,
    gbm.x = c(17,18,21), ## 11 variables
    gbm.y = 35,
    family = "bernoulli",
    tree.complexity = 5,
    learning.rate = 0.001,
    bag.fraction = 0.5)
```

### Get info in model output
```{r}
summary(brt.modelF3,
        cBars=length(brt.modelF3$var.names),
        n.trees=brt.modelF3$n.trees,
        plotit=TRUE,
        order=TRUE,
        method=relative.influence,
        normalize=FALSE)
```

### Save model output as external object for mapping later or posterity

```{r}
save(brt.modelF3, file = "../output/finalmodels_mt/BRTF3_model_data_output.rda")
```

```{r eval=FALSE, include=FALSE}
load(file = "../output/finalmodels_mt/BRTF3_model_data_output.rda")
```

### Relative influence of predictors as part of summary gbm - for model assessment
```{r}
relative.influence(brt.modelF3, scale=TRUE, sort=TRUE)
```

Notes: permutation.test.gbm(brt.model, n.trees=brt.model$n.trees); This method randomly permutes each predictor variable at a time and computes the associated reduction in predictive performance, similar to random forests. gbm.loss(y,f,w,offset,dist,baseline, group, max.rank)

### Plotting (Anna Added)
```{r}
gbm.plot(brt.modelF3, smooth=TRUE, write.title = FALSE)
dev.print(pdf, "../figs/finalmodels_mt/2019-09-05_BRT_modelF3_plots.pdf")
dev.off()
```
```{r}
gbm.plot.fits(brt.modelF3)
dev.print(pdf, "../figs/finalmodels_mt/2019-09-05_BRT_modelF3_fits_plots.pdf")
dev.off()
```

```{r}
find.int = gbm.interactions(brt.modelF3)
find.int$rank.list
find.int$interactions
```

## Calculate output stats 
- Sandra Haire calculations and file export below from Krawchuk et al. (2016) Ecosphere
Note that these calculatins are not the same as the default outputs from the BRT code.
```{r}
tot.n=nrow(model.data.hi)
y.perc=round(nrow(model.data.hi[model.data.hi$yvar==1,])/tot.n,2)
vnames=row.names(brt.modelF3$contributions)
rel.inf=round(brt.modelF3$contributions[,2],2) # variable num, from df and %contrib for each
perc.dev.expl=round(1-(brt.modelF3$self.statistics$mean.resid/brt.modelF3$self.statistics$mean.null),2)
roc.mean=round(mean(brt.modelF3$cv.roc.matrix),2)
cv.dev.mean=round(brt.modelF3$cv.statistics$deviance.mean,2)
cv.cor.mean=round(brt.modelF3$cv.statistics$correlation.mean,2)
cv.discrim.mean=round(brt.modelF3$cv.statistics$discrimination.mean,2)
```

```{r}
BRT.modelF3.sum=data.frame(tot.n, y.perc, brt.modelF3$n.trees, perc.dev.expl, roc.mean, cv.dev.mean, cv.cor.mean, cv.discrim.mean)
write.csv(BRT.modelF3.sum, '../output/finalmodels_mt/2019-09-05_BRT_modelF3_sum.csv', row.names = F)
BRT.modelF3.relinf=data.frame(rel.inf, vnames)
write.csv(BRT.modelF3.relinf, '../output/finalmodels_mt/2019-09-05_BRT_modelF3_relinf.csv', row.names = F)
```

```{r}
BRT.modelF3.sum
```

```{r}
BRT.modelF3.relinf
```

## Model F4: Split FWI - FWI Lo 
Run the BRT model with explanatory variables: dndmi (15), elevation(17), fwi (18), ndviprefire (21), rdnbr_class(26), reclass_rdnbr_mt (34), reclass_rdnbr_fs (35)

```{r}
set.seed(15) # Set random seed
brt.modelF4 <- gbm.step(data=model.data.lo,
    gbm.x = c(17,18,21), 
    gbm.y = 35,
    family = "bernoulli",
    tree.complexity = 5,
    learning.rate = 0.001,
    bag.fraction = 0.5)
```

### Get info in model output
```{r}
summary(brt.modelF4,
        cBars=length(brt.modelF4$var.names),
        n.trees=brt.modelF4$n.trees,
        plotit=TRUE,
        order=TRUE,
        method=relative.influence,
        normalize=FALSE)
```

### Save model output as external object for mapping later or posterity

```{r}
save(brt.modelF4, file = "../output/finalmodels_mt/BRTF4_model_data_output.rda")
```

```{r eval=FALSE, include=FALSE}
load(file = "../output/finalmodels_mt/BRTF4_model_data_output.rda")
```

### Relative influence of predictors as part of summary gbm - for model assessment
```{r}
relative.influence(brt.modelF4, scale=TRUE, sort=TRUE)
```

Notes: permutation.test.gbm(brt.model, n.trees=brt.model$n.trees); This method randomly permutes each predictor variable at a time and computes the associated reduction in predictive performance, similar to random forests. gbm.loss(y,f,w,offset,dist,baseline, group, max.rank)

### Plotting (Anna Added)
```{r}
gbm.plot(brt.modelF4, smooth=TRUE, write.title = FALSE)
dev.print(pdf, "../figs/finalmodels_mt/2019-09-05_BRT_modelF4_plots.pdf")
dev.off()
```
```{r}
gbm.plot.fits(brt.modelF4)
dev.print(pdf, "../figs/finalmodels_mt/2019-09-05_BRT_modelF4_fits_plots.pdf")
dev.off()
```

```{r}
find.int = gbm.interactions(brt.modelF4)
find.int$rank.list
find.int$interactions
```

## Calculate output stats 
- Sandra Haire calculations and file export below from Krawchuk et al. (2016) Ecosphere
Note that these calculatins are not the same as the default outputs from the BRT code.
```{r}
tot.n=nrow(model.data.lo)
y.perc=round(nrow(model.data.lo[model.data.lo$yvar==1,])/tot.n,2)
vnames=row.names(brt.modelF4$contributions)
rel.inf=round(brt.modelF4$contributions[,2],2) # variable num, from df and %contrib for each
perc.dev.expl=round(1-(brt.modelF4$self.statistics$mean.resid/brt.modelF4$self.statistics$mean.null),2)
roc.mean=round(mean(brt.modelF4$cv.roc.matrix),2)
cv.dev.mean=round(brt.modelF4$cv.statistics$deviance.mean,2)
cv.cor.mean=round(brt.modelF4$cv.statistics$correlation.mean,2)
cv.discrim.mean=round(brt.modelF4$cv.statistics$discrimination.mean,2)
```

```{r}
BRT.modelF4.sum=data.frame(tot.n, y.perc, brt.modelF4$n.trees, perc.dev.expl, roc.mean, cv.dev.mean, cv.cor.mean, cv.discrim.mean)
write.csv(BRT.modelF4.sum, '../output/finalmodels_mt/2019-09-05_BRT_modelF4_sum.csv', row.names = F)
BRT.modelF4.relinf=data.frame(rel.inf, vnames)
write.csv(BRT.modelF4.relinf, '../output/finalmodels_mt/2019-09-05_BRT_modelF4_relinf.csv', row.names = F)
```

```{r}
BRT.modelF4.sum
```

```{r}
BRT.modelF4.relinf
```

# MODEL F5 & F6 No split for weather

## Model F5: No split for weather 3 variables prefire veg, elevation, fwi
Run the BRT model with explanatory variables: dndmi (15), elevation(17), fwi (18), ndviprefire (21), rdnbr_class(26), reclass_rdnbr_mt (34), reclass_rdnbr_fs (35)

```{r}
set.seed(15) # Set random seed
brt.modelF5 <- gbm.step(data=model.data,
    gbm.x = c(17,18,21), 
    gbm.y = 35,
    family = "bernoulli",
    tree.complexity = 5,
    learning.rate = 0.001,
    bag.fraction = 0.5)
```

### Get info in model output
```{r}
summary(brt.modelF5,
        cBars=length(brt.modelF5$var.names),
        n.trees=brt.modelF5$n.trees,
        plotit=TRUE,
        order=TRUE,
        method=relative.influence,
        normalize=FALSE)
```

### Save model output as external object for mapping later or posterity

```{r}
save(brt.modelF5, file = "../output/finalmodels_mt/BRTF5_model_data_output.rda")
```

```{r eval=FALSE, include=FALSE}
load(file = "../output/finalmodels_mt/BRTF5_model_data_output.rda")
```

### Relative influence of predictors as part of summary gbm - for model assessment
```{r}
relative.influence(brt.modelF5, scale=TRUE, sort=TRUE)
```

Notes: permutation.test.gbm(brt.model, n.trees=brt.model$n.trees); This method randomly permutes each predictor variable at a time and computes the associated reduction in predictive performance, similar to random forests. gbm.loss(y,f,w,offset,dist,baseline, group, max.rank)

### Plotting (Anna Added)
```{r}
gbm.plot(brt.modelF5, smooth=TRUE, write.title = FALSE)
dev.print(pdf, "../figs/finalmodels_mt/2019-09-05_BRT_modelF5_plots.pdf")
dev.off()
```
```{r}
gbm.plot.fits(brt.modelF5)
dev.print(pdf, "../figs/finalmodels_mt/2019-09-05_BRT_modelF5_fits_plots.pdf")
dev.off()
```

```{r}
find.int = gbm.interactions(brt.modelF5)
find.int$rank.list
find.int$interactions
```

## Calculate output stats 
- Sandra Haire calculations and file export below from Krawchuk et al. (2016) Ecosphere
Note that these calculatins are not the same as the default outputs from the BRT code.
```{r}
tot.n=nrow(model.data)
y.perc=round(nrow(model.data[model.data$yvar==1,])/tot.n,2)
vnames=row.names(brt.modelF5$contributions)
rel.inf=round(brt.modelF5$contributions[,2],2) # variable num, from df and %contrib for each
perc.dev.expl=round(1-(brt.modelF5$self.statistics$mean.resid/brt.modelF5$self.statistics$mean.null),2)
roc.mean=round(mean(brt.modelF5$cv.roc.matrix),2)
cv.dev.mean=round(brt.modelF5$cv.statistics$deviance.mean,2)
cv.cor.mean=round(brt.modelF5$cv.statistics$correlation.mean,2)
cv.discrim.mean=round(brt.modelF5$cv.statistics$discrimination.mean,2)
```

```{r}
BRT.modelF5.sum=data.frame(tot.n, y.perc, brt.modelF5$n.trees, perc.dev.expl, roc.mean, cv.dev.mean, cv.cor.mean, cv.discrim.mean)
write.csv(BRT.modelF5.sum, '../output/finalmodels_mt/2019-09-05_BRT_modelF5_sum.csv', row.names = F)
BRT.modelF5.relinf=data.frame(rel.inf, vnames)
write.csv(BRT.modelF5.relinf, '../output/finalmodels_mt/2019-09-05_BRT_modelF5_relinf.csv', row.names = F)
```

```{r}
BRT.modelF5.sum
```

```{r}
BRT.modelF5.relinf
```

## Model F6: No split for weather four variable outbreak, prefire veg, fwi, elevation
Run the BRT model with explanatory variables: dndmi (15), elevation(17), fwi (18), ndviprefire (21), rdnbr_class(26), reclass_rdnbr_mt (34), reclass_rdnbr_fs (35)
```{r}
names(model.data)
```

```{r}
set.seed(15) # Set random seed
brt.modelF6 <- gbm.step(data=model.data,
    gbm.x = c(15,17,18,21), 
    gbm.y = 35,
    family = "bernoulli",
    tree.complexity = 5,
    learning.rate = 0.001,
    bag.fraction = 0.5)
```

### Get info in model output
```{r}
summary(brt.modelF6,
        cBars=length(brt.modelF6$var.names),
        n.trees=brt.modelF6$n.trees,
        plotit=TRUE,
        order=TRUE,
        method=relative.influence,
        normalize=FALSE)
```

### Save model output as external object for mapping later or posterity

```{r}
save(brt.modelF6, file = "../output/finalmodels_mt/BRTF6_model_data_output.rda")
```

```{r eval=FALSE, include=FALSE}
load(file = "../output/finalmodels_mt/BRTF6_model_data_output.rda")
```

### Relative influence of predictors as part of summary gbm - for model assessment
```{r}
relative.influence(brt.modelF6, scale=TRUE, sort=TRUE)
```

Notes: permutation.test.gbm(brt.model, n.trees=brt.model$n.trees); This method randomly permutes each predictor variable at a time and computes the associated reduction in predictive performance, similar to random forests. gbm.loss(y,f,w,offset,dist,baseline, group, max.rank)

### Plotting (Anna Added)
```{r}
gbm.plot(brt.modelF6, smooth=TRUE, write.title = TRUE, y.label="Fitted function", x.label="")
dev.print(pdf, "../figs/finalmodels_mt/2019-09-05_BRT_modelF6_plots.pdf")
dev.off()
```
```{r}
gbm.plot.fits(brt.modelF6)
dev.print(pdf, "../figs/finalmodels_mt/2019-09-05_BRT_modelF6_fits_plots.pdf")
dev.off()
```

```{r}
find.int = gbm.interactions(brt.modelF6)
find.int$rank.list
find.int$interactions
```

## Calculate output stats 
- Sandra Haire calculations and file export below from Krawchuk et al. (2016) Ecosphere
Note that these calculatins are not the same as the default outputs from the BRT code.
```{r}
tot.n=nrow(model.data)
y.perc=round(nrow(model.data[model.data$yvar==1,])/tot.n,2)
vnames=row.names(brt.modelF6$contributions)
rel.inf=round(brt.modelF6$contributions[,2],2) # variable num, from df and %contrib for each
perc.dev.expl=round(1-(brt.modelF6$self.statistics$mean.resid/brt.modelF6$self.statistics$mean.null),2)
roc.mean=round(mean(brt.modelF6$cv.roc.matrix),2)
cv.dev.mean=round(brt.modelF6$cv.statistics$deviance.mean,2)
cv.cor.mean=round(brt.modelF6$cv.statistics$correlation.mean,2)
cv.discrim.mean=round(brt.modelF6$cv.statistics$discrimination.mean,2)
```

```{r}
BRT.modelF6.sum=data.frame(tot.n, y.perc, brt.modelF6$n.trees, perc.dev.expl, roc.mean, cv.dev.mean, cv.cor.mean, cv.discrim.mean)
write.csv(BRT.modelF6.sum, '../output/finalmodels_mt/2019-09-05_BRT_modelF6_sum.csv', row.names = F)
BRT.modelF6.relinf=data.frame(rel.inf, vnames)
write.csv(BRT.modelF6.relinf, '../output/finalmodels_mt/2019-09-05_BRT_modelF6_relinf.csv', row.names = F)
```

```{r}
BRT.modelF6.sum
```

```{r}
BRT.modelF6.relinf
```


# MODEL F7, F8, F9: Remove prefire vegetation variable.


## Model F7: Split FWI - FWI HI 
Run the BRT model
with explanatory variables: dndmi (15), elevation(17), fwi (18), ndviprefire (21), rdnbr_class(26), reclass_rdnbr_mt (34), reclass_rdnbr_fs (35)

```{r}
set.seed(15) # Set random seed
brt.modelF7 <- gbm.step(data=model.data.hi,
    gbm.x = c(17,18,15), ## 11 variables
    gbm.y = 35,
    family = "bernoulli",
    tree.complexity = 5,
    learning.rate = 0.001,
    bag.fraction = 0.5)
```

### Get info in model output
```{r}
summary(brt.modelF7,
        cBars=length(brt.modelF7$var.names),
        n.trees=brt.modelF7$n.trees,
        plotit=TRUE,
        order=TRUE,
        method=relative.influence,
        normalize=FALSE)
```

### Save model output as external object for mapping later or posterity

```{r}
save(brt.modelF7, file = "../output/finalmodels/BRTF7_model_data_output.rda")
```

```{r eval=FALSE, include=FALSE}
load(file = "../output/finalmodels/BRTF7_model_data_output.rda")
```

### Relative influence of predictors as part of summary gbm - for model assessment
```{r}
relative.influence(brt.modelF7, scale=TRUE, sort=TRUE)
```

Notes: permutation.test.gbm(brt.model, n.trees=brt.model$n.trees); This method randomly permutes each predictor variable at a time and computes the associated reduction in predictive performance, similar to random forests. gbm.loss(y,f,w,offset,dist,baseline, group, max.rank)

### Plotting (Anna Added)
```{r}
gbm.plot(brt.modelF7, smooth=TRUE, write.title = FALSE)
dev.print(pdf, "../figures/finalmodels/2020-02-01_BRT_modelF7_plots.pdf")
dev.off()
```
```{r}
gbm.plot.fits(brt.modelF7)
dev.print(pdf, "../figures/finalmodels/2020-02-01_BRT_modelF7_fits_plots.pdf")
dev.off()
```

```{r}
find.int = gbm.interactions(brt.modelF7)
find.int$rank.list
find.int$interactions
```

## Calculate output stats 
- Sandra Haire calculations and file export below from Krawchuk et al. (2016) Ecosphere
Note that these calculatins are not the same as the default outputs from the BRT code.
```{r}
tot.n=nrow(model.data.hi)
y.perc=round(nrow(model.data.hi[model.data.hi$yvar==1,])/tot.n,2)
vnames=row.names(brt.modelF7$contributions)
rel.inf=round(brt.modelF7$contributions[,2],2) # variable num, from df and %contrib for each
perc.dev.expl=round(1-(brt.modelF7$self.statistics$mean.resid/brt.modelF7$self.statistics$mean.null),2)
roc.mean=round(mean(brt.modelF7$cv.roc.matrix),2)
cv.dev.mean=round(brt.modelF7$cv.statistics$deviance.mean,2)
cv.cor.mean=round(brt.modelF7$cv.statistics$correlation.mean,2)
cv.discrim.mean=round(brt.modelF7$cv.statistics$discrimination.mean,2)
```

```{r}
BRT.modelF7.sum=data.frame(tot.n, y.perc, brt.modelF7$n.trees, perc.dev.expl, roc.mean, cv.dev.mean, cv.cor.mean, cv.discrim.mean)
write.csv(BRT.modelF7.sum, '../output/finalmodels/2020-02-01_BRT_modelF7_sum.csv', row.names = F)
BRT.modelF7.relinf=data.frame(rel.inf, vnames)
write.csv(BRT.modelF7.relinf, '../output/finalmodels/2020-02-01_BRT_modelF7_relinf.csv', row.names = F)
```

```{r}
BRT.modelF7.sum
```

```{r}
BRT.modelF7.relinf
```

## Model F8: Split FWI - FWI Lo 
Run the BRT model with explanatory variables: dndmi (15), elevation(17), fwi (18), ndviprefire (21), rdnbr_class(26), reclass_rdnbr_mt (34), reclass_rdnbr_fs (35)

```{r}
set.seed(15) # Set random seed
brt.modelF8 <- gbm.step(data=model.data.lo,
    gbm.x = c(17,18,15), 
    gbm.y = 35,
    family = "bernoulli",
    tree.complexity = 5,
    learning.rate = 0.001,
    bag.fraction = 0.5)
```

### Get info in model output
```{r}
summary(brt.modelF8,
        cBars=length(brt.modelF8$var.names),
        n.trees=brt.modelF8$n.trees,
        plotit=TRUE,
        order=TRUE,
        method=relative.influence,
        normalize=FALSE)
```

### Save model output as external object for mapping later or posterity

```{r}
save(brt.modelF8, file = "../output/finalmodels/BRTF8_model_data_output.rda")
```

```{r eval=FALSE, include=FALSE}
load(file = "../output/finalmodels/BRTF8_model_data_output.rda")
```

### Relative influence of predictors as part of summary gbm - for model assessment
```{r}
relative.influence(brt.modelF8, scale=TRUE, sort=TRUE)
```

Notes: permutation.test.gbm(brt.model, n.trees=brt.model$n.trees); This method randomly permutes each predictor variable at a time and computes the associated reduction in predictive performance, similar to random forests. gbm.loss(y,f,w,offset,dist,baseline, group, max.rank)

### Plotting (Anna Added)
```{r}
gbm.plot(brt.modelF8, smooth=TRUE, write.title = FALSE)
dev.print(pdf, "../figures/finalmodels/2020-02-01_BRT_modelF8_plots.pdf")
dev.off()
```
```{r}
gbm.plot.fits(brt.modelF8)
dev.print(pdf, "../figures/finalmodels/2020-02-01_BRT_modelF8_fits_plots.pdf")
dev.off()
```

```{r}
find.int = gbm.interactions(brt.modelF8)
find.int$rank.list
find.int$interactions
```

## Calculate output stats 
- Sandra Haire calculations and file export below from Krawchuk et al. (2016) Ecosphere
Note that these calculatins are not the same as the default outputs from the BRT code.
```{r}
tot.n=nrow(model.data.lo)
y.perc=round(nrow(model.data.lo[model.data.lo$yvar==1,])/tot.n,2)
vnames=row.names(brt.modelF8$contributions)
rel.inf=round(brt.modelF8$contributions[,2],2) # variable num, from df and %contrib for each
perc.dev.expl=round(1-(brt.modelF8$self.statistics$mean.resid/brt.modelF8$self.statistics$mean.null),2)
roc.mean=round(mean(brt.modelF8$cv.roc.matrix),2)
cv.dev.mean=round(brt.modelF8$cv.statistics$deviance.mean,2)
cv.cor.mean=round(brt.modelF8$cv.statistics$correlation.mean,2)
cv.discrim.mean=round(brt.modelF8$cv.statistics$discrimination.mean,2)
```

```{r}
BRT.modelF8.sum=data.frame(tot.n, y.perc, brt.modelF8$n.trees, perc.dev.expl, roc.mean, cv.dev.mean, cv.cor.mean, cv.discrim.mean)
write.csv(BRT.modelF8.sum, '../output/finalmodels/2020-02-01_BRT_modelF8_sum.csv', row.names = F)
BRT.modelF8.relinf=data.frame(rel.inf, vnames)
write.csv(BRT.modelF8.relinf, '../output/finalmodels/2020-02-01_BRT_modelF8_relinf.csv', row.names = F)
```

```{r}
BRT.modelF8.sum
```

```{r}
BRT.modelF8.relinf
```

## Model F9: No split for weather 3 variables outbreak, elevation, fwi
Run the BRT model with explanatory variables: dndmi (15), elevation(17), fwi (18), ndviprefire (21), rdnbr_class(26), reclass_rdnbr_mt (34), reclass_rdnbr_fs (35)

```{r}
set.seed(15) # Set random seed
brt.modelF9 <- gbm.step(data=model.data,
    gbm.x = c(17,18,15), 
    gbm.y = 35,
    family = "bernoulli",
    tree.complexity = 5,
    learning.rate = 0.001,
    bag.fraction = 0.5)
```

### Get info in model output
```{r}
summary(brt.modelF9,
        cBars=length(brt.modelF9$var.names),
        n.trees=brt.modelF9$n.trees,
        plotit=TRUE,
        order=TRUE,
        method=relative.influence,
        normalize=FALSE)
```

### Save model output as external object for mapping later or posterity

```{r}
save(brt.modelF9, file = "../output/finalmodels/BRTF9_model_data_output.rda")
```

```{r eval=FALSE, include=FALSE}
load(file = "../output/finalmodels/BRTF9_model_data_output.rda")
```

### Relative influence of predictors as part of summary gbm - for model assessment
```{r}
relative.influence(brt.modelF9, scale=TRUE, sort=TRUE)
```

Notes: permutation.test.gbm(brt.model, n.trees=brt.model$n.trees); This method randomly permutes each predictor variable at a time and computes the associated reduction in predictive performance, similar to random forests. gbm.loss(y,f,w,offset,dist,baseline, group, max.rank)

### Plotting (Anna Added)
```{r}
gbm.plot(brt.modelF9, smooth=TRUE, write.title = FALSE)
dev.print(pdf, "../figures/finalmodels/2020-02-01_BRT_modelF9_plots.pdf")
dev.off()
```
```{r}
gbm.plot.fits(brt.modelF9)
dev.print(pdf, "../figures/finalmodels/2020-02-01_BRT_modelF9_fits_plots.pdf")
dev.off()
```

```{r}
find.int = gbm.interactions(brt.modelF9)
find.int$rank.list
find.int$interactions
```

## Calculate output stats 
- Sandra Haire calculations and file export below from Krawchuk et al. (2016) Ecosphere
Note that these calculatins are not the same as the default outputs from the BRT code.
```{r}
tot.n=nrow(model.data)
y.perc=round(nrow(model.data[model.data$yvar==1,])/tot.n,2)
vnames=row.names(brt.modelF9$contributions)
rel.inf=round(brt.modelF9$contributions[,2],2) # variable num, from df and %contrib for each
perc.dev.expl=round(1-(brt.modelF9$self.statistics$mean.resid/brt.modelF9$self.statistics$mean.null),2)
roc.mean=round(mean(brt.modelF9$cv.roc.matrix),2)
cv.dev.mean=round(brt.modelF9$cv.statistics$deviance.mean,2)
cv.cor.mean=round(brt.modelF9$cv.statistics$correlation.mean,2)
cv.discrim.mean=round(brt.modelF9$cv.statistics$discrimination.mean,2)
```

```{r}
BRT.modelF9.sum=data.frame(tot.n, y.perc, brt.modelF9$n.trees, perc.dev.expl, roc.mean, cv.dev.mean, cv.cor.mean, cv.discrim.mean)
write.csv(BRT.modelF9.sum, '../output/finalmodels/2020-02-01_BRT_modelF9_sum.csv', row.names = F)
BRT.modelF9.relinf=data.frame(rel.inf, vnames)
write.csv(BRT.modelF9.relinf, '../output/finalmodels/2020-02-01_BRT_modelF9_relinf.csv', row.names = F)
```

```{r}
BRT.modelF9.sum
```

```{r}
BRT.modelF9.relinf
```
**THE END**