---
title: "BRT Continuous Response"
author: "Anna Talucci"
date: "4/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

Model with RdNBR as a continuous response variable

## Notes

--Beetle vs. Fuels

Boosted Regression Trees in R 
Note: this is a cut-down version of a tutorial prepared by Jane Elith and John Leathwick
Adapted by Chris Dunn for fire risk assessment
Adapted by Garrett Meigs for analysis of fire refugia
Complementary to Krawchuk et al. 2016 Ecosphere scripts

## Clear workspace

```{r}
rm(list=ls()) 
```

## Set libraries

```{r message=FALSE, warning=FALSE}
library(devtools)
library(gbm)
library(foreign)
library(dismo)
library(dplyr)
library(splines)
library(ggplot2)
```

## Install additional BRT functions 
These are provided in a file such as ?brt.functions.R? and can be loaded into R using the source command, e.g.:
```{r}
source("../function/brt.functions.R")
```

## Import data
```{r}
model.data = read.csv("../data/GRTS_Samples/2019-09-02_AllSamples.csv", header=TRUE, sep = ",", strip.white = TRUE)
```

## Check dimensions, column names and order for later operations, and summary statistics
```{r}
head(model.data)
```

```{r}
summary(model.data$ndviprefire)
```

```{r}
summary(model.data$dndmi)
```
```{r}
summary(model.data$rdnbr)
```

```{r}
summary(model.data$elevation)
```

```{r}
summary(model.data$fwi)
```


```{r}
dim(model.data)
```
```{r}
hist(model.data$fwi)
```

```{r}
dim(model.data)
```


```{r}
head(model.data)
```

```{r}
names(model.data)
```

# MODEL
 
Run the BRT model with RdNBR as continuous
with explanatory variables (column number): 
*  elevation (17), 
*  fwi (18), 
*  dndmibeetle (15)
*  ndviprefire (21), 
*  rdnbr (23)

```{r}
set.seed(15) # Set random seed
brt.model99 <- gbm.step(data=model.data,
    gbm.x = c(15,17, 18, 21), 
    gbm.y = 23,
    family = "gaussian",
    tree.complexity = 5,
    learning.rate = 0.001,
    bag.fraction = 0.5)
```

### Get info in model output
```{r}
summary(brt.model99,
        cBars=length(brt.model99$var.names),
        n.trees=brt.model99$n.trees,
        plotit=TRUE,
        order=TRUE,
        method=relative.influence,
        normalize=FALSE)
```

### Save model output as external object for mapping later or posterity

```{r}
save(brt.model99, file = "../output/finalmodels/BRT_model_ContRdNBR_output.rda")
```

```{r eval=FALSE, include=FALSE}
load(file = "../output/finalmodels/BRT_model_ContRdNBR_output.rda")
```

### Relative influence of predictors as part of summary gbm - for model assessment
```{r}
relative.influence(brt.model99, scale=TRUE, sort=TRUE)
```

Notes: permutation.test.gbm(brt.model, n.trees=brt.model$n.trees); This method randomly permutes each predictor variable at a time and computes the associated reduction in predictive performance, similar to random forests. gbm.loss(y,f,w,offset,dist,baseline, group, max.rank)


```{r eval=FALSE, include=FALSE}
gbm.plot(brt.model99, smooth=TRUE, write.title = FALSE)
dev.print(pdf, "../figs/finalmodels_mt/2019-05-22_BRT_model99_plots.pdf")
dev.off()
```
```{r eval=FALSE, include=FALSE}
gbm.plot.fits(brt.model99)
dev.print(pdf, "../figs/finalmodels_mt/2019-05-22_BRT_model99_fits_plots.pdf")
dev.off()
```

```{r}
find.int = gbm.interactions(brt.model99)
find.int$rank.list
find.int$interactions
```


**THE END**