---
title: "Partial Plots"
author: "Anna Talucci"
date: "01-22-2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview
Script adapted from Areil Muldoon and Garrett Meigs

September 2019: Extra fun with partial plots.  This script is designed to use brt model runs saved as .Rdas.

# Goal: Overlay partial-dependence plots from multiple models.

NOte: the y-axis of the BRT model are referred to as the fitted function, for a binomial distribtuion this fitted function is the loggit scale. To convert back to a probability we can use the plogis() function. We will leave the y-axix on the logit scale but also add a line for a high probability

setwd("K:/Papers/Meigs_Refugia2_LateSuccessionalForests/r_files_brt")   ### Change to wherever you put the code files sourced below

# Load packages
```{r message=FALSE, warning=FALSE}
library(gbm)
library(dismo)
library(purrr) # for looping
library(ggplot2)
library(scales)
library(dplyr) # for data manip
library(cowplot)
```

# BRT Models

Model         | Group   | FWI          | Explanatory Variables
------------- | --------| ------------ | -------------------------------------------
brt.model1.1  |    1    | Extreme FWI  | Prefire, outbreak, weather, topography
brt.model1.2  |    1    | Moderate FWI | Prefire, outbreak, weather, topography
brt.model1.3  |    1    | Full FWI     | Prefire, outbreak, weather, topography
brt.model2.1  |    2    | Extreme FWI  | Prefire, weather, topography
brt.model2.2  |    2    | Moderate FWI | Prefire, weather, topography
brt.model2.3  |    2    | Full FWI     | Prefire,  weather, topography
brt.model3.1  |    3    | Extreme FWI  | Outbreak, weather, topography
brt.model3.2  |    3    | Moderate FWI | Outbreak, weather, topography
brt.model3.3  |    3    | Full FWI     | Outbreak, weather, topography




# Load BRT Models 
Load BRT models that are saved during the model as .Rda files in the working directory. Models are assembled and run in the script 'BRTAnalyses'
```{r}
load(file = "../output/finalmodels_mt/BRT1.1_model_data_output.rda")
brt.model1.1 = brt.model1.1

load(file = "../output/finalmodels_mt/BRT1.2_model_data_output.rda")
brt.model1.2 = brt.model1.2

load(file = "../output/finalmodels_mt/BRT1.3_model_data_output.rda")
brt.model1.3 = brt.model1.3

load(file = "../output/finalmodels_mt/BRT2.1_model_data_output.rda")
brt.model2.1 = brt.model2.1

load(file = "../output/finalmodels_mt/BRT2.2_model_data_output.rda")
brt.model2.2 = brt.model2.2

load(file = "../output/finalmodels_mt/BRT2.3_model_data_output.rda")
brt.model2.3 = brt.model2.3

load(file = "../output/finalmodels_mt/BRT3.1_model_data_output.rda")
brt.model3.1 = brt.model3.1

load(file = "../output/finalmodels_mt/BRT3.2_model_data_output.rda")
brt.model3.2 = brt.model3.2

load(file = "../output/finalmodels_mt/BRT3.3_model_data_output.rda")
brt.model3.3 = brt.model3.3
```

# Y-axis as probability instead of Fitted function
```{r}
prob_yaxis = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9)
fitted_yaxis = qlogis(prob_yaxis)
fitted_yaxis
```


# Manuscript figure

## Group 1 models 
Make list of models and variables
```{r}
group1 = list(grp1_extrm = brt.model1.1, grp1_mod = brt.model1.2, grp1_full = brt.model1.3)
group1_vars = c("dndmi", "elevation", "fwi", "ndviprefire")
names(group1_vars) = group1_vars
group1_vars
```

Nicer variable names for x axis labels Must be in same order as vars
```{r}
group1_x_names = c("dNDMI", "Elevation (m)", "FWI", "NDVI")
```

### Predicted dataset 
Use nested loops for each variable and then each model within each variable

 For outer loop use map() or lapply()
 For the inner loop use imap_dfr() to use models and model names and bind together

 Work out approach with a single variable
 Goal is to get a dataset with predictions from all models stacked together for one x variable

### Loop through single varible
```{r}
pred_test4 = map(group1_vars[[1]], function(variable) {
     imap_dfr(group1, function(Model, mod.name) {
          preddat = plot.gbm(Model, i.var = variable, return.grid = TRUE)
          preddat$center_y = scale(preddat$y, scale = FALSE)
          preddat$x = preddat[, 1]
          preddat$Model = mod.name
          preddat
     })
})

pred_test4
```

### Loop through all Varaibles 
If that worked, loop through all variables
```{r}
pred_group1 = map(group1_vars, function(variable) {
     imap_dfr(group1, function(model, mod.name) {
          preddat = plot.gbm(model, i.var = variable, return.grid = TRUE)
          preddat$center_y = scale(preddat$y, scale = FALSE)
          preddat$x = preddat[, 1]
          preddat$model = mod.name
          preddat
     })
})
```

Figure out plot limits (if want all the same) by binding all groups together and calculating min and max center_y
```{r}
range(bind_rows(pred_group1)$center_y)
```

### Plot with improved x axis names ----
```{r}
model_id_grp1 <- ggplot(data = pred_group1[[1]], aes(x = x, y = center_y, linetype = model, color = model) ) +
        geom_smooth(span = 0.5, se = FALSE) + # choose span? 
        scale_color_manual(values = c(grp1_full="blue",grp1_extrm="red", grp1_mod="orange"), name = "Fire weather", guide = guide_legend(reverse=TRUE)) +
        scale_linetype_manual(values = c(grp1_full="solid", grp1_extrm="longdash", grp1_mod="twodash"), name = "Fire weather", guide = guide_legend(reverse=TRUE)) +
        labs(x = group1_x_names[[1]]) +
        theme_bw(base_size = 12) +
        theme(axis.text.x = element_text(size = 10, color = "black"),
              axis.text.y = element_text(size = 10, color = "black"),
              panel.border = element_rect(color = "black", size = 1.25),
              panel.grid.major = element_line(color = 'white', linetype = 'dashed'), panel.grid.minor = element_blank(),
              legend.position = "bottom",
              legend.title = element_text(size = 14),
              legend.text = element_text(size = 14)) +
        scale_x_continuous(labels = scales::format_format(scientific = FALSE)) +
        #scale_x_continuous(labels = comma) +
        #ylim(-1.55, 1.55) +
        geom_hline(yintercept=0)+
        scale_y_continuous(limits=c(-2.2,2.2), breaks=c(-2.1972246, -1.3862944, -0.8472979, -0.4054651,  0.0000000,  0.4054651,  0.8472979,  1.3862944, 2.1972246), labels = c("0.1", "", "0.3","", "0.5","", "0.7","", "0.9"), name="Probability")

model_id_grp1
```
Leaving legend to indicate multiple models plotted.

### Figure Legend
```{r}
BC_leg = ggplot(data = pred_group1[[1]], aes(x = x, y = center_y, linetype = model, color = model) ) +
        geom_smooth(span = 0.5, se = FALSE) + # choose span? 
        scale_color_manual(values = c(grp1_full="blue",grp1_extrm="red", grp1_mod="orange"), breaks=c("grp1_full","grp1_extrm","grp1_mod"), name = "Burning conditions", labels=c(grp1_full="Full",grp1_extrm="Extreme", grp1_mod="Moderate"), guide = guide_legend(reverse=FALSE)) +
        scale_linetype_manual(values = c(grp1_full="solid", grp1_extrm="longdash", grp1_mod="twodash"), breaks=c("grp1_full","grp1_extrm","grp1_mod"), name = "Burning conditions", labels=c(grp1_full="Full",grp1_extrm="Extreme", grp1_mod="Moderate"), guide = guide_legend(reverse=FALSE)) +
        labs(y = "Fitted Function",
             x = group1_x_names[[1]]) +
        theme_bw(base_size = 12) +
        theme(axis.text.x = element_text(size = 10, color = "black"),
              axis.text.y = element_text(size = 10, color = "black"),
              panel.border = element_rect(color = "black", size = 1.25),
              panel.grid.major = element_line(color = 'white', linetype = 'dashed'), panel.grid.minor = element_blank(),
              legend.position = "right",
              legend.title = element_text(size = 14),
              legend.text = element_text(size = 14)) +
        scale_x_continuous(labels = scales::format_format(scientific = FALSE)) +
        #scale_x_continuous(labels = comma) +
        #ylim(-1.55, 1.55) +
        geom_hline(yintercept=0)+
        scale_y_continuous(limits=c(-2.2,2.2), breaks=c(-2.1972246, -1.3862944, -0.8472979, -0.4054651,  0.0000000,  0.4054651,  0.8472979,  1.3862944, 2.1972246), labels = c("0.1", "", "0.3","", "0.5","", "0.7","", "0.9"), name="Probability")

BC_leg
```

### Plotting function ----
Note: plot.margin - t,r,b,l

Adjust plot margins for compiling a panel figure with cowplot.

```{r}
pardep_plot_group1 = function(data, x_var) {
     ggplot(data = data, aes(x = x, y = center_y, linetype = model, color = model) ) +
                geom_smooth(span = 0.5, se = FALSE) + # choose span? 
                scale_color_manual(values = c(grp1_full="blue",grp1_extrm="red", grp1_mod="orange"), name = "Burning conditions", labels=c("Full", "Extreme", "Moderate"), guide = guide_legend(reverse=FALSE)) +
        scale_linetype_manual(values = c(grp1_full="solid", grp1_extrm="longdash", grp1_mod="twodash"), name = "Burning conditions", labels=c("Full", "Extreme", "Moderate"), guide = guide_legend(reverse=FALSE)) +
                labs(x = x_var) +
                theme_bw(base_size = 12) +
                theme(plot.margin = unit(c(0.05, 0.2, 0.05, 0.5), "cm")) +
                theme(axis.text.x = element_text(size = 10, color = "black"),
                      axis.text.y = element_text(size = 10, color = "black"),
                      panel.border = element_rect(color = "black", size = 1.25),
                      panel.grid.major = element_line(color = 'white', linetype = 'dashed'), panel.grid.minor = element_blank(),
                      legend.position = "none") +
                scale_x_continuous(labels = scales::format_format(scientific = FALSE)) +
                #scale_x_continuous(labels = comma) +
                #ylim(-1.55, 1.55) +
                geom_hline(yintercept=0)+
                scale_y_continuous(limits=c(-2.2,2.2), breaks=c(-2.1972246, -1.3862944, -0.8472979, -0.4054651,  0.0000000,  0.4054651,  0.8472979,  1.3862944, 2.1972246), labels = c("0.1", "", "0.3","", "0.5","", "0.7","", "0.9"), name="Probability")
}

pardep_plot_group1(data = pred_group1[[1]], x_var = group1_x_names[[1]])
```

### Loop through the models and the x variable names
    simultaneously with map2()
```{r}
group1_all_plots = map2(pred_group1, group1_x_names, pardep_plot_group1)
group1_all_plots
```



## Group 2 models 

Make list of models and variables
```{r}
group2 = list(grp2_extrm = brt.model2.1, grp2_mod = brt.model2.2, grp2_full = brt.model2.3)
group2_vars = c("elevation", "fwi", "ndviprefire")
names(group2_vars) = group2_vars
group2_vars
```

Nicer variable names for x axis labels Must be in same order as vars
```{r}
group2_x_names = c("Elevation (m)", "FWI", "NDVI")
```

### Use nested loops for each variable and then each model within each variable

 For outer loop use map() or lapply()
 For the inner loop use imap_dfr() to use models and model names and bind together

 Work out approach with a single variable
 Goal is to get a dataset with predictions from all models stacked together for one x variable

```{r}
pred_test3 = map(group2_vars[[1]], function(variable) {
     imap_dfr(group2, function(Model, mod.name) {
          preddat = plot.gbm(Model, i.var = variable, return.grid = TRUE)
          preddat$center_y = scale(preddat$y, scale = FALSE)
          preddat$x = preddat[, 1]
          preddat$Model = mod.name
          preddat
     })
})

pred_test3
```



### Loop through all variables

```{r}
pred_group2 = map(group2_vars, function(variable) {
     imap_dfr(group2, function(model, mod.name) {
          preddat = plot.gbm(model, i.var = variable, return.grid = TRUE)
          preddat$center_y = scale(preddat$y, scale = FALSE)
          preddat$x = preddat[, 1]
          preddat$model = mod.name
          preddat
     })
})
```

Figure out plot limits (if want all the same) by binding all groups together and calculating min and max center_y
```{r}
range(bind_rows(pred_group2)$center_y)
```

### Plot with improved x axis names ----

```{r}
model_id_grp2 <- ggplot(data = pred_group2[[1]], aes(x = x, y = center_y, linetype = model, color = model) ) +
        geom_smooth(span = 0.5, se = FALSE) + # choose span? 
        scale_color_manual(values = c(grp2_full="blue",grp2_extrm="red", grp2_mod="orange"), name = "Burning conditions", labels=c("Full", "Extreme", "Moderate"), guide = guide_legend(reverse=FALSE)) +
        scale_linetype_manual(values = c(grp2_full="solid", grp2_extrm="longdash", grp2_mod="twodash"), name = "Burning conditions", labels=c("Full", "Extreme", "Moderate"), guide = guide_legend(reverse=FALSE)) +
        labs( x = group2_x_names[[1]]) +
        theme_bw(base_size = 14) +
        theme(axis.text.x = element_text(size = 14, color = "black"),
              axis.text.y = element_text(size = 14, color = "black"),
              panel.border = element_rect(color = "black", size = 1.25),
              panel.grid.major = element_line(color = 'white', linetype = 'dashed'), panel.grid.minor = element_blank(),
              legend.position = "bottom",
              legend.title = element_text(size = 14),
              legend.text = element_text(size = 14)) +
        scale_x_continuous(labels = scales::format_format(scientific = FALSE)) +
        #scale_x_continuous(labels = comma) +
        #ylim(-1.55, 1.55) +
        geom_hline(yintercept=0)+
        scale_y_continuous(limits=c(-2.2,2.2), breaks=c(-2.1972246, -1.3862944, -0.8472979, -0.4054651,  0.0000000,  0.4054651,  0.8472979,  1.3862944, 2.1972246), labels = c("0.1", "", "0.3","", "0.5","", "0.7","", "0.9"), name="Probability")

model_id_grp2
```
Leaving legend to indicate multiple models plotted.

### Plotting function ----
note plot.margin - t,r,b,l
```{r}
pardep_plot_group2 = function(data, x_var) {
     ggplot(data = data, aes(x = x, y = center_y, linetype = model, color = model) ) +
                geom_smooth(span = 0.5, se = FALSE) + # choose span? 
                scale_color_manual(values = c(grp2_full="blue",grp2_extrm="red", grp2_mod="orange"), name = "Burning conditions", labels=c("Full", "Extreme", "Moderate"), guide = guide_legend(reverse=FALSE)) +
        scale_linetype_manual(values = c(grp2_full="solid", grp2_extrm="longdash", grp2_mod="twodash"), name = "Burning conditions", labels=c("Full", "Extreme", "Moderate"), guide = guide_legend(reverse=FALSE)) +
                labs(x = x_var) +
                theme_bw(base_size = 12) +
                theme(plot.margin = unit(c(0.05, 0.2, 0.05, 0.5), "cm")) +
                theme(axis.text.x = element_text(size = 10, color = "black"),
                      axis.text.y = element_text(size = 10, color = "black"),
                      panel.border = element_rect(color = "black", size = 1.25),
                      panel.grid.major = element_line(color = 'white', linetype = 'dashed'), panel.grid.minor = element_blank(),
                      legend.position = "none") +
                scale_x_continuous(labels = scales::format_format(scientific = FALSE)) +
                #scale_x_continuous(labels = comma) +
                #ylim(-1.55, 1.55) +
                geom_hline(yintercept=0)+
                scale_y_continuous(limits=c(-2.2,2.2), breaks=c(-2.1972246, -1.3862944, -0.8472979, -0.4054651,  0.0000000,  0.4054651,  0.8472979,  1.3862944, 2.1972246), labels = c("0.1", "", "0.3","", "0.5","", "0.7","", "0.9"), name="Probability")
}

pardep_plot_group2(data = pred_group2[[1]], x_var = group2_x_names[[1]])
```


### Loop through the models and the x variable names
    simultaneously with map2()
```{r}
group2_all_plots = map2(pred_group2, group2_x_names, pardep_plot_group2)
group2_all_plots
```


## Group 3 Models - Outbreak Severity, Elelvatio, Fire Weather
Make list of models and variables
```{r}
group3 = list(grp3_extrm = brt.model3.1, grp3_mod = brt.model3.2, grp3_full = brt.model3.3)
group3_vars = c("elevation", "fwi", "dndmi")
names(group3_vars) = group3_vars
group3_vars
```

Nicer variable names for x axis labels Must be in same order as vars
```{r}
group3_x_names = c("Elevation (m)", "FWI", "dNDMI")
```

### Use nested loops for each variable and then each model within each variable

 For outer loop use map() or lapply()
 For the inner loop use imap_dfr() to use models and model names and bind together

 Work out approach with a single variable
 Goal is to get a dataset with predictions from all models stacked together for one x variable

```{r}
pred_test_group3 = map(group3_vars[[1]], function(variable) {
     imap_dfr(group3, function(Model, mod.name) {
          preddat = plot.gbm(Model, i.var = variable, return.grid = TRUE)
          preddat$center_y = scale(preddat$y, scale = FALSE)
          preddat$x = preddat[, 1]
          preddat$Model = mod.name
          preddat
     })
})

pred_test_group3
```


### Loop through all variables
```{r}
pred_group3 = map(group3_vars, function(variable) {
     imap_dfr(group3, function(model, mod.name) {
          preddat = plot.gbm(model, i.var = variable, return.grid = TRUE)
          preddat$center_y = scale(preddat$y, scale = FALSE)
          preddat$x = preddat[, 1]
          preddat$model = mod.name
          preddat
     })
})
```

Figure out plot limits (if want all the same) by binding all groups together and calculating min and max center_y
```{r}
range(bind_rows(pred_group3)$center_y)
```

### Plot with improved x axis names ----

```{r}
model_id_grp3 <- ggplot(data = pred_group3[[1]], aes(x = x, y = center_y, linetype = model, color = model) ) +
        geom_smooth(span = 0.5, se = FALSE) + # choose span? 
        scale_color_manual(values = c(grp3_full="blue",grp3_extrm="red", grp3_mod="orange"), name = "Burning conditions", labels=c("Full", "Extreme", "Moderate"), guide = guide_legend(reverse=FALSE)) +
        scale_linetype_manual(values = c(grp3_full="solid", grp3_extrm="longdash", grp3_mod="twodash"), name = "Burning conditions", labels=c("Full", "Extreme", "Moderate"), guide = guide_legend(reverse=FALSE)) +
        labs(x = group3_x_names[[1]]) +
        theme_bw(base_size = 14) +
        theme(axis.text.x = element_text(size = 14, color = "black"),
              axis.text.y = element_text(size = 14, color = "black"),
              panel.border = element_rect(color = "black", size = 1.25),
              panel.grid.major = element_line(color = 'white', linetype = 'dashed'), panel.grid.minor = element_blank(),
              legend.position = "bottom",
              legend.title = element_text(size = 14),
              legend.text = element_text(size = 14)) +
        scale_x_continuous(labels = scales::format_format(scientific = FALSE)) +
        #scale_x_continuous(labels = comma) +
        #ylim(-1.55, 1.55) +
        geom_hline(yintercept=0)+
         scale_y_continuous(limits=c(-2.2,2.2), breaks=c(-2.1972246, -1.3862944, -0.8472979, -0.4054651,  0.0000000,  0.4054651,  0.8472979,  1.3862944, 2.1972246), labels = c("0.1", "", "0.3","", "0.5","", "0.7","", "0.9"), name="Probability")
model_id_grp3
```
Leaving legend to indicate multiple models plotted.

### Plotting function ----
note plot.margin - t,r,b,l
```{r}
pardep_plot_group3 = function(data, x_var) {
     ggplot(data = data, aes(x = x, y = center_y, linetype = model, color = model) ) +
                geom_smooth(span = 0.5, se = FALSE) + # choose span? 
                scale_color_manual(values = c(grp3_full="blue",grp3_extrm="red", grp3_mod="orange"), name = "Burning conditions", labels=c("Full", "Extreme", "Moderate"), guide = guide_legend(reverse=FALSE)) +
        scale_linetype_manual(values = c(grp3_full="solid", grp3_extrm="longdash", grp3_mod="twodash"), name = "Burning conditions", labels=c("Full", "Extreme", "Moderate"), guide = guide_legend(reverse=FALSE)) +
                labs(x = x_var) +
                theme_bw(base_size = 12) +
                theme(plot.margin = unit(c(0.05, 0.2, 0.05, 0.5), "cm")) +
                theme(axis.text.x = element_text(size = 10, color = "black"),
                      axis.text.y = element_text(size = 10, color = "black"),
                      panel.border = element_rect(color = "black", size = 1.25),
                      panel.grid.major = element_line(color = 'white', linetype = 'dashed'), panel.grid.minor = element_blank(),
                      legend.position = "none") +
                scale_x_continuous(labels = scales::format_format(scientific = FALSE)) +
                #scale_x_continuous(labels = comma) +
                #ylim(-1.55, 1.55) +
                geom_hline(yintercept=0)+
                scale_y_continuous(limits=c(-2.2,2.2), breaks=c(-2.1972246, -1.3862944, -0.8472979, -0.4054651,  0.0000000,  0.4054651,  0.8472979,  1.3862944, 2.1972246), labels = c("0.1", "", "0.3","", "0.5","", "0.7","", "0.9"), name="Probability")
}

pardep_plot_group3(data = pred_group3[[1]], x_var = group3_x_names[[1]])
```




### Loop through the models and the x variable names
    simultaneously with map2()
```{r}
group3_all_plots = map2(pred_group3, group3_x_names, pardep_plot_group3)
group3_all_plots
```


# Panel Figures

## Headers and Legend

```{r}
grp1 = ggdraw() + draw_label('Group 1', size = 12, fontface = 'bold') 
grp2 = ggdraw() + draw_label('Group 2', size = 12, fontface = 'bold')
grp3 = ggdraw() + draw_label('Group 3', size = 12, fontface = 'bold')

header_groups = cowplot::plot_grid(grp1, grp2, grp3, ncol=3)
header_groups
```




## Manuscript Figure: Groups

Order plots
-- FWI
-- Elevation
-- NDVI
-- dNDMI

### Legends

```{r}
legendman <- get_legend(BC_leg) 
```
### Group 1
```{r fig.height=7, fig.width=2}
grp1 = cowplot::plot_grid( group1_all_plots$fwi, group1_all_plots$elevation, group1_all_plots$ndviprefire,group1_all_plots$dndmi, ncol = 1) +
    draw_label("moderate", x = .49, y = .835, size = 9) +
   draw_label("extreme", x = .83, y = .835, size = 9) +
       draw_label("low", x = .41, y = .585, size = 9) +
   draw_label("high", x = .84, y = .585, size = 9) +
   draw_label("dead", x = .43, y = .335, size = 9) +
   draw_label("live", x = .83, y = .335, size = 9) +
   draw_label("low", x = .53, y = .085, size = 9) +
   draw_label("high", x = .83, y = .085, size = 9) +

   draw_label("(a)", x = .4, y = .98, size = 10) +
   draw_label("(b)", x = .4, y = .73, size = 10) +
   draw_label("(c)", x = .4, y = .48, size = 10) +
   draw_label("(d)", x = .4, y = .23, size = 10) 

grp1
```

### Group 2
```{r fig.height=7, fig.width=2}
grp2 = cowplot::plot_grid(group2_all_plots$fwi, group2_all_plots$elevation, group2_all_plots$ndviprefire, legendman, ncol = 1) +
    draw_label("moderate", x = .49, y = .835, size = 9) +
   draw_label("extreme", x = .83, y = .835, size = 9) +
       draw_label("low", x = .41, y = .585, size = 9) +
   draw_label("high", x = .84, y = .585, size = 9) +
   draw_label("dead", x = .43, y = .335, size = 9) +
   draw_label("live", x = .83, y = .335, size = 9) +


   draw_label("(e)", x = .40, y = .98, size = 10) +
   draw_label("(f)", x = .40, y = .73, size = 10) +
   draw_label("(g)", x = .40, y = .48, size = 10) 
grp2
```



### Group 3
```{r fig.height=7, fig.width=2}
grp3 = cowplot::plot_grid( group3_all_plots$fwi, group3_all_plots$elevation, NULL, group3_all_plots$dndmi, ncol = 1) + 
    draw_label("moderate", x = .49, y = .835, size = 9) +
   draw_label("extreme", x = .83, y = .835, size = 9) +
       draw_label("low", x = .41, y = .585, size = 9) +
   draw_label("high", x = .84, y = .585, size = 9) +
   draw_label("low", x = .53, y = .085, size = 9) +
   draw_label("high", x = .83, y = .085, size = 9) +


   draw_label("(h)", x = .40, y = .98, size = 10) +
   draw_label("(i)", x = .40, y = .73, size = 10) +
   draw_label("(j)", x = .40, y = .23, size = 10) 
grp3
```

### Combine groups
```{r fig.height=7, fig.width=6}
( grid_groups = cowplot::plot_grid(grp1, grp2, grp3, ncol=3) )
```
```{r fig.height=7, fig.width=6}
( grid_group_head = cowplot::plot_grid(header_groups, grid_groups, ncol=1, rel_heights = c(0.04, 1))  )
```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/2021-01-21_partialplots_MTBreaks_probability.png", plot =   grid_group_head, width = 6, height = 7, units = c("in"), dpi=600 )
```





**THE END**