---
title: "CBI versus Burn Severity"
author: "Anna Talucci"
date: "October 16, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(statmod)
library(car)
library(DHARMa)
library(GGally)
library(MASS)
library(cowplot)
library(magick)
library(maptree)
library(cluster)

library(ggrepel)
library(rattle)
library(rpart.plot)
library(RColorBrewer)
library(party)
library(cluster)
```


# Data

## Field Data
### Site info
```{r}
chfield = read.csv("../data/field-sites/2019-02-15_field_sites_beetle_chzone10.csv", header=TRUE, sep = ",", strip.white = TRUE)

head(chfield)
```

```{r}
enfield = read.csv("../data/field-sites/2019-02-15_field_sites_beetle_enzone10.csv", header=TRUE, sep = ",", strip.white = TRUE)

head(enfield)
```

```{r}
twfield = read.csv("../data/field-sites/2019-02-15_field_sites_beetle_zone9.csv", header=TRUE, sep = ",", strip.white = TRUE)

head(twfield)
```
### Field measures
```{r}
field_data = read.csv("../data/field-sites/field_plot_tree_surface.csv", header=TRUE, sep = ",", strip.white = TRUE)

head(field_data)
```

```{r}
field_data = rename(field_data, plot_id=Plot_ID)
```

### CBI Data

```{r}
cbi = read.csv("../data/field-sites/2018-12-10_Entiako_CBI.csv", header = TRUE, sep = ",", strip.white = TRUE)
```

```{r}
head(cbi)

```

```{r}
(extrac = cbi %>%
  dplyr::select(plot:prefiredead, Fire, UTM.E:UTM.N, CBI.under:CBI.total))
```


```{r eval=FALSE, include=FALSE}
write.csv(extrac, "../output/2018-12-10_entiakoCBI_subset.csv", quote = TRUE, row.names = FALSE, sep = ",")
```


## CBI plus GEE data

```{r}
cbigee = read.csv("../data/gee/2018-12-11_encbi-gee.csv", header = TRUE, sep = ",", strip.white = TRUE)
```

```{r}
head(cbigee)
```
```{r}
unique(cbigee$CBI_total)
```


```{r}

cbigee1 = cbigee %>% mutate("severity"= 
                    ifelse(between(CBI_total, 0,0.10),"unchanged",
                    ifelse(between(CBI_total,0.11,1.24),"low",
                    ifelse(between(CBI_total,1.25,2.24),"moderate",
                    ifelse(between(CBI_total,2.25,3.0),"high","NON"))))) %>% dplyr::select(CBI_over:Fire, severity, dnbr:rdnbr)

```

```{r}
str(cbigee)
```

## GEE Data
```{r}
chgee = read.csv("../data/gee/2019-04-04_chfieldsites10.csv", header=TRUE, sep = ",", strip.white = TRUE)

head(chgee)
```

```{r}
engee = read.csv("../data/gee/2019-04-04_enfieldsites10.csv", header=TRUE, sep = ",", strip.white = TRUE)

head(engee)
```

```{r}
twgee = read.csv("../data/gee/2019-04-04_twfieldsites9.csv", header=TRUE, sep = ",", strip.white = TRUE)

head(twgee)
```

## Combine gee data sets
```{r}
gee = rbind(chgee, engee, twgee)
gee
```
### add field data to gee
```{r}

gee_field16 = merge(gee, field_data, by="plot_id")
```

```{r}
head(gee_field16)
```
### Define Class Levels

```{r}
gee$fire_sever = factor(gee$fire_sever,levels=c("High","Moderate","Low", "unburned"), ordered=TRUE)
```

### Figure

#### Scatter Plots

##### NDVI v RdNBR
```{r}
fslegend = ggplot(gee, aes(x=ndviprefire, y=rdnbr, color=fire_sever)) +
  geom_point() +
  scale_color_manual(values = c("#ff5733",  "#ffc300", "#daf7a6", "#1f618d"), name="",
                         breaks=c("High", "Moderate", "Low", "unburned"),
                         labels=c("High", "Moderate", "Low", "Unburned")) +
    ylab(label="RdNBR") + 
  xlab("NDVI") +
  geom_hline(aes(yintercept=316), colour="darkorange2", linetype="dotdash", size=1)  +
   geom_hline(aes(yintercept=640), colour="darkorange2", linetype="dotdash", size=1)  +
  theme_bw() +
   theme(legend.position = "bottom") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))

fslegend
```

```{r}
( scatplot1 = ggplot(gee, aes(x=ndviprefire, y=rdnbr, color=fire_sever)) +
  geom_point() +
  scale_color_manual(values = c("#ff5733",  "#ffc300", "#daf7a6", "#1f618d"), name="",
                         breaks=c("High", "Moderate", "Low", "unburned"),
                         labels=c("High", "Moderate", "Low", "Unburned")) +
    ylab(label="RdNBR") + 
  xlab("NDVI") +
  geom_hline(aes(yintercept=600), colour="darkorange2", linetype="dotdash", size=1)  +
  theme_bw() +
   theme(legend.position = "none") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) )
```

##### Field v RdNBR
```{r}
ggplot(gee_field16, aes(x=soil.sur, y=rdnbr, color=fire_sever)) +
  geom_point() +
  scale_color_manual(values = c("#ff5733",  "#ffc300", "#daf7a6", "#1f618d"), name="",
                         breaks=c("High", "Moderate", "Low", "unburned"),
                         labels=c("High", "Moderate", "Low", "Unburned")) +
    ylab(label="RdNBR") + 
  xlab("soil") +
  geom_hline(aes(yintercept=600), colour="darkorange2", linetype="dotdash", size=1)  +
  theme_bw() +
   theme(legend.position = "none") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) 
```

```{r}
ggplot(gee_field16, aes(x=FIRE, y=rdnbr, color=fire_sever)) +
  geom_point() +
  scale_color_manual(values = c("#ff5733",  "#ffc300", "#daf7a6", "#1f618d"), name="",
                         breaks=c("High", "Moderate", "Low", "unburned"),
                         labels=c("High", "Moderate", "Low", "Unburned")) +
    ylab(label="RdNBR") + 
  xlab("fire killed") +
  geom_hline(aes(yintercept=600), colour="darkorange2", linetype="dotdash", size=1)  +
  theme_bw() +
   theme(legend.position = "none") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) 
```

```{r}
ggplot(gee_field16, aes(x=none, y=rdnbr, color=fire_sever)) +
  geom_point() +
  scale_color_manual(values = c("#ff5733",  "#ffc300", "#daf7a6", "#1f618d"), name="",
                         breaks=c("High", "Moderate", "Low", "unburned"),
                         labels=c("High", "Moderate", "Low", "Unburned")) +
    ylab(label="RdNBR") + 
  xlab("canopy") +
  geom_hline(aes(yintercept=600), colour="darkorange2", linetype="dotdash", size=1)  +
  theme_bw() +
   theme(legend.position = "none") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) 
```

```{r}
ggplot(gee_field16, aes(x=DC3, y=rdnbr, color=fire_sever)) +
  geom_point() +
  scale_color_manual(values = c("#ff5733",  "#ffc300", "#daf7a6", "#1f618d"), name="",
                         breaks=c("High", "Moderate", "Low", "unburned"),
                         labels=c("High", "Moderate", "Low", "Unburned")) +
    ylab(label="RdNBR") + 
  xlab("deep char") +
  geom_hline(aes(yintercept=600), colour="darkorange2", linetype="dotdash", size=1)  +
  theme_bw() +
   theme(legend.position = "none") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) 
```
##### CBI v RdNBR
```{r}
ggplot(cbigee1, aes(x=CBI_total, y=rdnbr, color=severity)) +
  geom_point() +
    ylab(label="RdNBR") + 
  xlab("CBI") +
  
  scale_color_manual(values = c("#ff5733",  "#ffc300", "#daf7a6", "#1f618d"), name="",
                         breaks=c("high", "moderate", "low", "unchanged"),
                         labels=c("High", "Moderate", "Low", "Unburned")) +
  geom_hline(aes(yintercept=316), colour="darkorange2", linetype="dotdash", size=1)  +
  geom_hline(aes(yintercept=640), colour="darkorange2", linetype="dotdash", size=1)  +
  theme_bw() +
   theme(legend.position = "bottom") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))


```

##### CBI v RdNBR
```{r fig.height=4, fig.width=6}
cbi_rdnbr_plot = ggplot(cbigee1, aes( x=rdnbr,y=CBI_total, color=severity)) +
  geom_point() +
    xlab(label="RdNBR") + 
  ylab("CBI") +
  
  scale_color_manual(values = c("#ff5733",  "#ffc300", "#daf7a6", "#1f618d"), name="CBI severity class",
                         breaks=c("high", "moderate", "low", "unchanged"),
                         labels=c("High", "Moderate", "Low", "Unburned")) +
  geom_hline(aes(yintercept=2.25), colour="gray50", linetype="longdash", size=1)  +
   annotate(geom="text", label=2.25, x=0, y=2.25, vjust=-.5, color="gray50") +
  geom_vline(aes(xintercept=641), colour="gray50", linetype="solid", size=1)  +
   annotate(geom="text", label=641, x=641, y=0.1, vjust=-.5, color="gray50", angle=90) +
  theme_bw() +
   theme(legend.position = "bottom") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))

cbi_rdnbr_plot
```
```{r eval=FALSE, include=FALSE}
ggsave("../figures/2021-01-30_CBI_RdNBR.png", plot = cbi_rdnbr_plot, width = 6, height = 4, units = c("in"), dpi=600 )
```

```{r}
cbigee1 %>% dplyr::select(rdnbr, CBI_over:CBI_under, severity) %>% filter(CBI_total >= 2.0)
```

```{r}
y = -369.0 + 421.7*exp(2.25*0.388)
y
```

```{r}
cbigee1 %>% dplyr::select(severity, rdnbr, CBI_total) %>% mutate(predicted = -369.0 + 421.7*exp(CBI_total*0.388)) %>% mutate(difference = rdnbr-predicted)  %>% filter(CBI_total >= 2.0)
```

##### CBI v dnbr
```{r}
ggplot(cbigee, aes(x=CBI_total, y=dnbr, color=sev_cat)) +
  geom_point() +
    ylab(label="RdNBR") + 
  xlab("CBI") +
  scale_color_manual(values = c("#ff5733",  "#ffc300", "#daf7a6", "#1f618d"), name="",
                         breaks=c("high", "moderate", "low", "unchanged"),
                         labels=c("High", "Moderate", "Low", "Unburned")) +
  geom_hline(aes(yintercept=177), colour="darkorange2", linetype="dotdash", size=1)  +
  geom_hline(aes(yintercept=367), colour="darkorange2", linetype="dotdash", size=1)  +
  theme_bw() +
   theme(legend.position = "bottom") +
    theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
    theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))


```
(x = reorder(Species, Sepal.Width, FUN = median)(x=reorder(fire_sever, rdnbr, FUN = median)
```{r}
gee$fire_sever
```

#### Box plot of fire severity classes
```{r}
(boxplot1 = ggplot(gee, aes(x=fire_sever, y=rdnbr, fill=fire_sever, order=fire_sever)) +
  geom_boxplot() +
  scale_fill_manual(values = c("#ff5733", "#ffc300", "#daf7a6", "#1f618d"), name="") +
   scale_x_discrete(                         breaks=c("High", "Moderate", "Low", "unburned"),
                         labels=c("High", "Moderate", "Low", "Unburned"))+
    ylab(label="RdNBR") + 
  xlab("Burn severity class") +
   guides(fill=guide_legend(ncol=2)) +
  theme_bw(base_size = 12) +
                theme(plot.margin = unit(c(0.05, 0.2, 0.05, 0.5), "cm")) +
   theme(legend.position = "none") +

    theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) )
```



```{r fig.height=4, fig.width=6}
legend = cowplot::get_legend(fslegend)
( fscombo1=cowplot::plot_grid(scatplot1, boxplot1, labels = c("A", "B"), align = "hv", ncol= 2)  ) 
(fscombo2 = plot_grid(fscombo1, legend, ncol=1, rel_widths = c(1, .1), rel_heights = c(1, .05)) ) 
```

```{r eval=FALSE, include=FALSE}
ggsave("../figs/2019-04-08_2016_field.jpeg", plot = fscombo2, width = 6, height = 4, units = c("in"), dpi=600 )
```


```{r}
head(gee)
```


# RdNBR Miller & Thode only
```{r warning=FALSE,message=FALSE,echo=FALSE}
graph11 = ggplot(data = cbigee, aes(x = CBI_total , y = rdnbr)) +
         geom_point(size = 2) +
          ylab("RdNBR") +
          xlab("Total CBI")  +
    theme_bw(base_size = 12) +
                theme(plot.margin = unit(c(0.05, 0.2, 0.05, 0.5), "cm")) +

  geom_hline(aes(yintercept=600), colour="darkorange2", linetype="dotdash", size=1)  +
          theme_bw() 
```
Break points from Reilly et al. - red dashed line RdNBR = 235 and RdNBR = 649.
Break points from Miller and Thode - orange dot dashed line RdNBR =  and RdNBR = 649.

```{r warning=FALSE,message=FALSE,echo=FALSE}
graph12 = ggplot(data = cbigee, aes(x = CBI_over , y = rdnbr)) +
         geom_point(size = 2) +
          ylab("RdNBR") +
          xlab("Over-story CBI")  +
    theme_bw(base_size = 12) +
                theme(plot.margin = unit(c(0.05, 0.2, 0.05, 0.5), "cm")) +
  geom_hline(aes(yintercept=600), colour="darkorange2", linetype="dotdash", size=1)  +
            theme_bw() 
```
Break points from Reilly et al. - red dash line is at dNBR = 235 and orange dotdash is as dNBR = 649.

```{r warning=FALSE,message=FALSE,echo=FALSE}
graph13 = ggplot(data = cbigee, aes(x = CBI_under , y = rdnbr)) +
         geom_point(size = 2) +
          ylab("RdNBR") +
          xlab("Under-story CBI")  +
    theme_bw(base_size = 12) +
                theme(plot.margin = unit(c(0.05, 0.2, 0.05, 0.5), "cm")) +
  geom_hline(aes(yintercept=600), colour="darkorange2", linetype="dotdash", size=1)  +
            theme_bw() 
```


```{r fig.height=4.5, fig.width=6}
( combo1=cowplot::plot_grid(graph11, graph12, graph13, labels = c("A", "B", "C"), align = "hv", ncol= 2)  ) 
```

```{r eval=FALSE, include=FALSE}
ggsave("../figs/2019-04-08_CBI_Entiako.jpeg", plot = combo1, width = 6, height = 5, units = c("in"), dpi=600 )
```

```{r fig.height=4.5, fig.width=6}
( combo1=cowplot::plot_grid(graph11, graph12, graph13, boxplot1, labels = c("A", "B", "C", "D"), align = "hv", ncol= 2)  ) 
```

```{r eval=FALSE, include=FALSE}
ggsave("../figs/2019-05-01_CBIen_allfield.tiff", plot = combo1, width = 6, height = 4.5, units = c("in"), dpi=600 )
```

```{r fig.height=4.5, fig.width=6}
( combo2=cowplot::plot_grid(graph11, graph12, graph13, boxplot1, labels = c("(a)", "(b)", "(c)", "(d)"), label_fontface = 'plain', label_size = 12, align = "hv", ncol= 2)  ) 
```
```{r eval=FALSE, include=FALSE}
ggsave("../figs/2019-09-27_CBIen_BS_field.tiff", plot = combo2, width = 6, height = 4.5, units = c("in"), dpi=600 )
```
# CART
```{r}
frmla1 = fire_sever ~ rdnbr + ndviprefire  

fit1 = rpart(frmla1, method="class", data=gee)
```

```{r}
tr1 = tree(frmla1, data=gee)
```

```{r}
summary(tr1)
```

```{r}
plot(tr1); text(tr1, all = T) 
```

```{r}
frmla2 = fire_sever ~ dnbr + ndviprefire  

fit2 = rpart(frmla1, method="class", data=gee)
```

```{r}
tr2 = tree(frmla2, data=gee)
```

```{r}
summary(tr2)
```

```{r}
plot(tr2); text(tr2, all = T) 
```

```{r}
head(gee)
```

```{r}
( gee_sub = gee %>% dplyr::select(dnbr, ndviprefire, rdnbr, fire_sever) )

```
```{r}
# K-Means Cluster Analysis
set.seed(20)
fit1 <- kmeans(gee_sub[, 1], 4) # 5 cluster solution
fit1
```

```{r}
table(fit1$cluster, gee_sub$fire_sever)
```

```{r}
fit1$cluster = as.factor(fit1$cluster)
ggplot(gee_sub, aes(x=ndviprefire, y=dnbr, color = fit1$cluster, shape=fire_sever)) + 
  geom_point() +
  geom_hline(aes(yintercept=500), colour="#990000", linetype="dashed", size=1)  +
  geom_hline(aes(yintercept=350), colour="darkorange2", linetype="dotdash", size=1) 
```


```{r}
# K-Means Cluster Analysis
set.seed(20)
fit2 <- kmeans(gee_sub[, 3], 4) # 5 cluster solution
fit2
```

```{r}
table(fit2$cluster, gee_sub$fire_sever)
```

```{r}
fit2$cluster = as.factor(fit2$cluster)
ggplot(gee_sub, aes(x=ndviprefire, y=rdnbr, color = fit2$cluster, shape=fire_sever)) + 
  geom_point() +
  geom_hline(aes(yintercept=600), colour="#990000", linetype="dashed", size=1)  +
  geom_hline(aes(yintercept=649), colour="darkorange2", linetype="dotdash", size=1)  
  
```



**THE END**