---
title: "Climate Moisture Deficit"
author: "Anna Talucci"
date: "April 4, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

Climate moisture deficit (CMD) as an indicator of anomalously warm and dry fire weather conditions
Thinking about Climatic anomalies that influence fire weather in sub-boreal



# Packages

The following Packages are required for the below analyses:

```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(MASS)
library(car)
library(GGally)
library(lme4)
library(DHARMa)
library(lsmeans)
library(gmodels)
library(REdaS)
library(RColorBrewer)
library(cowplot)
library(forcats)
```

# Data extract and organize
## 2016 BC Climate data 

```{r}
c2016 = read.csv("../data/climate/2016_climate.csv", header=TRUE, sep = ",", strip.white = TRUE)
head(c2016)
```

```{r}
(c2016 = c2016 %>%
   mutate(year = "2016") %>% dplyr::select(plot:Longitude, CMD01:CMD12, year) %>%
  mutate(sum_cmd2016 = CMD01+CMD02+CMD03+CMD04+CMD05+CMD06+CMD07+CMD08+CMD09+CMD10+CMD11+CMD12))
```

```{r}
names(c2016)[6:17] = c("CMD01.2016", "CMD02.2016", "CMD03.2016", "CMD04.2016", "CMD05.2016", "CMD06.2016", "CMD07.2016", "CMD08.2016", "CMD09.2016", "CMD10.2016", "CMD11.2016", "CMD12.2016")

head(c2016)
```

## 2015 BC Climate data 
```{r}
c2015 = read.csv("../data/climate/2015_climate.csv", header=TRUE, sep = ",", strip.white = TRUE)
head(c2015)
```

```{r}
c2015 = c2015 %>%
   mutate(year = "2015") %>% dplyr::select(plot:Longitude, CMD01:CMD12, year) %>%
    mutate(sum_cmd2015 = CMD01+CMD02+CMD03+CMD04+CMD05+CMD06+CMD07+CMD08+CMD09+CMD10+CMD11+CMD12)

names(c2015)[6:17] = c( "CMD01.2015", "CMD02.2015", "CMD03.2015", "CMD04.2015", "CMD05.2015", "CMD06.2015", "CMD07.2015", "CMD08.2015", "CMD09.2015", "CMD10.2015", "CMD11.2015", "CMD12.2015")

head(c2015)
```




## 2014 BC Climate data 
```{r}
c2014 = read.csv("../data/climate/2014_climate.csv", header=TRUE, sep = ",", strip.white = TRUE)
head(c2014)
```

```{r}
c2014 = c2014 %>%
   mutate(year = "2014") %>% dplyr::select(plot:Longitude, CMD01:CMD12, year) %>%
    mutate(sum_cmd2014 = CMD01+CMD02+CMD03+CMD04+CMD05+CMD06+CMD07+CMD08+CMD09+CMD10+CMD11+CMD12)

names(c2014)[6:17] = c( "CMD01.2014", "CMD02.2014", "CMD03.2014", "CMD04.2014", "CMD05.2014", "CMD06.2014", "CMD07.2014", "CMD08.2014", "CMD09.2014", "CMD10.2014", "CMD11.2014", "CMD12.2014")

head(c2014)
```



## 2013 BC Climate data 
```{r}
c2013 = read.csv("../data/climate/2013_climate.csv", header=TRUE, sep = ",", strip.white = TRUE)
head(c2013)
```

```{r}
(c2013 = c2013 %>%
   mutate(year = "2013") %>% dplyr::select(plot:Longitude, CMD01:CMD12, year) %>%
    mutate(sum_cmd2013 = CMD01+CMD02+CMD03+CMD04+CMD05+CMD06+CMD07+CMD08+CMD09+CMD10+CMD11+CMD12))
```

```{r}
names(c2013)[6:17] = c( "CMD01.2013", "CMD02.2013", "CMD03.2013", "CMD04.2013", "CMD05.2013", "CMD06.2013", "CMD07.2013", "CMD08.2013", "CMD09.2013", "CMD10.2013", "CMD11.2013", "CMD12.2013")

head(c2013)
```

## 2012 BC Climate data 
```{r}
c2012 = read.csv("../data/climate/2012_climate.csv", header=TRUE, sep = ",", strip.white = TRUE)
head (c2012)
```

```{r}
(c2012 = c2012 %>%
   mutate(year = "2012") %>% dplyr::select(plot:Longitude, CMD01:CMD12, year) %>%
    mutate(sum_cmd2012 = CMD01+CMD02+CMD03+CMD04+CMD05+CMD06+CMD07+CMD08+CMD09+CMD10+CMD11+CMD12))
```

```{r}
names(c2012)[6:17] = c( "CMD01.2012", "CMD02.2012", "CMD03.2012", "CMD04.2012", "CMD05.2012", "CMD06.2012", "CMD07.2012", "CMD08.2012", "CMD09.2012", "CMD10.2012", "CMD11.2012", "CMD12.2012")

head(c2012)
```

## 2012 BC Climate data 
```{r}
c2011 = read.csv("../data/climate/2011_climate.csv", header=TRUE, sep = ",", strip.white = TRUE)
head (c2011)
```

```{r}
(c2011 = c2011 %>%
   mutate(year = "2011") %>% dplyr::select(plot:Longitude, CMD01:CMD12, year) %>%
   mutate(sum_cmd2011 = CMD01+CMD02+CMD03+CMD04+CMD05+CMD06+CMD07+CMD08+CMD09+CMD10+CMD11+CMD12))
```

```{r}
names(c2011)[6:17] = c( "CMD01.2011", "CMD02.2011", "CMD03.2011", "CMD04.2011", "CMD05.2011", "CMD06.2011", "CMD07.2011", "CMD08.2011", "CMD09.2011", "CMD10.2011", "CMD11.2011", "CMD12.2011")

head(c2012)
```

## Merge climate data
```{r}
climate.1112 = merge(c2011, c2012, by = c("plot", "ID1", "ID2", "Latitude", "Longitude"))
head(climate.1112)
```

```{r}
climate.1314 = merge(c2013, c2014, by = c("plot", "ID1", "ID2", "Latitude", "Longitude"))
head(climate.1314)
```

```{r}
climate.1516 = merge(c2015, c2016, by = c("plot", "ID1", "ID2", "Latitude", "Longitude"))
head(climate.1516)
```

```{r}
climate.11121314 = merge(climate.1112, climate.1314, by = c("plot", "ID1", "ID2", "Latitude", "Longitude"))
head(climate.11121314)
```

```{r}
cmd_11_16 = merge(climate.11121314, climate.1516, by = c("plot", "ID1", "ID2", "Latitude", "Longitude"))
head(cmd_11_16)
```


# Climate Normal Data

```{r}
norm61 = read.csv("../data/climate/climate_normal1961-2000.csv", header=TRUE, sep = ",", strip.white = TRUE)
head(norm61)

```

```{r}
norm81 = read.csv("../data/climate/climate_normal_1981-2000.csv", header=TRUE, sep = ",", strip.white = TRUE)
head(norm81)
```

```{r}
summarise(norm81, mean(MAT, na.rm = T))
summarise(norm81, mean(MAP))
summarise(norm81, mean(MSP))
summarise(norm81, mean(MWMT))
summarise(norm81, mean(MCMT))
summarise(norm81, min(Elevation))
summarise(norm81, max(Elevation))
```



```{r}
norm81 = norm81 %>% dplyr::select(plot:Longitude, CMD)
norm61 = norm61 %>% dplyr::select(plot:Longitude, CMD)
```

```{r}
( climate_normal = merge(norm61, norm81, by = c("plot", "ID1", "ID2", "Latitude", "Longitude")) )
climate_normal
```

```{r}
names(climate_normal)[6:7] = c("cmd.norm61", "cmd.norm81")
head(climate_normal)
```

```{r}
( climate_cmd = merge(climate_normal, cmd_11_16, by = c("plot", "ID1", "ID2", "Latitude", "Longitude")) )
climate_cmd
```


```{r}
cmd = climate_cmd %>% dplyr::select(sum_cmd2011, sum_cmd2012, sum_cmd2013, sum_cmd2014, sum_cmd2015, sum_cmd2016, cmd.norm61, cmd.norm81)
head(cmd)

```


```{r}

( legend = ggplot(stack(cmd), aes(x = ind, y = values, fill = ind)) +
  geom_boxplot() +
  scale_fill_brewer(palette = "Accent", name = "Year", breaks=c("sum_cmd2011", "sum_cmd2012", "sum_cmd2013", "sum_cmd2014", "sum_cmd2015", "sum_cmd2016", "cmd.norm61", "cmd.norm81"),
                         labels=c("2011", "2012", "2013", "2014", "2015", "2016", "1961-2000", "1981-2010")) +
theme_bw() +

  
      ylab("Climate moisture deficit (mm)") +
    xlab("") +
  scale_x_discrete(breaks=c("sum_cmd2011", "sum_cmd2012", "sum_cmd2013", "sum_cmd2014", "sum_cmd2015", "sum_cmd2016", "cmd.norm61", "cmd.norm81"),
                         labels=c("2011", "2012", "2013", "2014", "2015", "2016", "1961-2000", "1981-2010")) )
```


```{r}
cmd_sub = climate_cmd %>% dplyr::select(sum_cmd2012, sum_cmd2013, sum_cmd2014, cmd.norm81)
head(cmd_sub)

```


```{r fig.height=4, fig.width=6}

(climatecmd = ggplot(stack(cmd_sub), aes(x = ind, y = values, fill = ind)) +
  geom_boxplot() +
  scale_fill_brewer(palette = "Accent", name = "Year", 
                    breaks=c("sum_cmd2012", "sum_cmd2013", "sum_cmd2014", "cmd.norm81"),
                         labels=c("2012", "2013", "2014", "1981-2010")) +
  theme_bw() +
  ylab("Climate moisture deficit (mm)") +
  xlab("") +
  scale_x_discrete(breaks=c("sum_cmd2012", "sum_cmd2013", "sum_cmd2014", "cmd.norm81"),
                         labels=c("2012", "2013", "2014", "1981-2010")) )
```

```{r eval=FALSE, include=FALSE}
ggsave("../figs/2019-04-26_climateCMD.tiff", plot = climatecmd, width = 6, height = 4, units = c("in"), dpi=600 )
```


```{r}
cmd_sub2 = climate_cmd %>% dplyr::select(sum_cmd2012, sum_cmd2013, sum_cmd2014, cmd.norm81)
head(cmd_sub)

```


```{r}
cmd3 = cmd_sub2 %>% dplyr::select(sum_cmd2012, sum_cmd2013, sum_cmd2014, cmd.norm81)
head(cmd3)
cmd4=cmd3 %>% gather(key = cmd_period, value=mm)
head(cmd4)
```
 pasgraph = ggplot(pas2, aes(x = reorder(snow_period, mm, FUN=median), y = mm, fill = snow_period))
```{r}
cmd4$cmd_period=factor(cmd4$cmd_period , levels=levels(cmd4$cmd_period)[c("cmd.norm81","sum_cmd2012","sum_cmd2013","sum_cmd2014")])
```

ggplot(cmd4, aes(x = reorder(cmd_period, mm, FUN=median), y = mm, fill = cmd_period))
```{r fig.height=4, fig.width=6}

(climatecmd2 = ggplot(cmd4, aes(x = cmd_period, y = mm, fill = cmd_period)) +
  geom_boxplot() +
  scale_fill_brewer(palette = "Accent", name = "Year", 
                    breaks=c("sum_cmd2012", "sum_cmd2013", "sum_cmd2014", "cmd.norm81"),
                         labels=c("2012", "2013", "2014", "1981-2010")) +
  theme_bw() +
      theme(legend.position = "none") +
  ylab("Climate moisture deficit (mm)") +
  xlab("") +
  scale_x_discrete(breaks=c( "cmd.norm81", "sum_cmd2012", "sum_cmd2013", "sum_cmd2014"),
                         labels=c("1981-2010", "2012", "2013", "2014")) )
```

```{r eval=FALSE, include=FALSE}
ggsave("../figs/2019-04-26_climateCMD_ordered.tiff", plot = climatecmd2, width = 6, height = 4, units = c("in"), dpi=600 )
```

```{r fig.height=6, fig.width=6}
legend = cowplot::get_legend(legend)

( climatenorm = cowplot::plot_grid(frostgraph, pasgraph, cmdgraph, legend, labels = c("A", "B", "C"), align = "hv", ncol= 2) )
```


