---
title: "Scatter plots of predictor variables"
author: "Anna Talucci"
date: "February 7, 2019"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview
Evaluate correlation between explanatory and predictor variables for BRT models.

# Packages
```{r}
library(devtools)
library(gbm)
library(foreign)
library(dismo)
library(corrplot)
library(dplyr)
```


# Data
```{r}
model.data = read.csv("../data/GRTS_Samples/2019-09-02_AllSamples.csv", header=TRUE, sep = ",", strip.white = TRUE)
```


# Check Data
Chaeck data dimensions, column names and order for later operations, and summary statistics
```{r}
head(model.data)
```


# Subset Veg predictor varaibles
```{r}
plot.data= dplyr::select(model.data, dndmi, ndviprefire, elevation, rdnbr)
head(plot.data)
```


# Scatterplot matrix to evaluate covaration among predictors.  Simple graph requires calling variables by name.
```{r}
pairs(~rdnbr + elevation + ndviprefire + dndmi, data = plot.data, lower.panel = NULL, cex.labels = 4, cex.axis = 4) #Could include title
dev.print(pdf, "../output/2021-01-25_scatter_veg.pdf", width = 40, height = 40)
dev.off()
```

# Correlation matrices thanks to: https://cran.r-project.org/web/packages/corrplot/vignettes/corrplot-intro.html
```{r}
cor <- cor(plot.data)
corrplot.mixed(cor, lower = "number", upper = "ellipse", number.cex = 1.2, tl.col = "black" , lower.col = "black")
dev.print(pdf, "../output/2021-01-25_variable_corrplots.pdf", width = 12, height = 12)
dev.off()
```


cor(mtcars, use="complete.obs", method="kendall") 
```{r}
cor(plot.data, use="complete.obs", method="pearson")
```


**THE END**